Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
nudge

Given a model for a plant for which to synthesise a controller, provided in
an ANSI-C input file (Steps 1--3), DSSynth constructs a non-deterministic
model to represent the plant family (Step~A), and formulates a function
(step~B) using implementation details provided in Steps~$2$ and $3$ to
calculate the parameters of the controller to be synthesised (Step~C). 
Finally, DSSynth builds an intermediate ANSI-C code for the digital system
implementation, which is used as input for the CEGIS engine (Step~D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
property of interst (i.e., robust stability) and is passed to
CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive
Synthesis (CEGIS) module, where the controller is marked as input variable
to synthesise.  The properties specified in the ANSI-C code model can only
be satisfied if CEGIS synthesises controller coefficients that
satisfy~$\phi$.  CEGIS employs an iterative, counterexample-guided
refinement process which is explained in detail in
section~\ref{synthesiser-general}.  A successful synthesis result is
reported if CEGIS generates a controllerthat is safe with respect to~$\phi$. 
In particular, the ANSI-C code model guarantees that a synthesised solution
is complete and sound with respect to stability property~$\phi$, since it
does not depend on system inputs and outputs.  In the case of stability, the
specification~$\phi$ consists in a number of assumptions on the polynomial
coefficients, following Jury's Criteria, as well as the restrictions set in
the representation of these coefficients.

>>>>

Given a model for a plant for which to synthesise a controller, provided in
an ANSI-C input file (Steps 1--3), DSSynth constructs a non-deterministic
model to represent the plant family (Step~A), and formulates a function
(Step~B) using implementation details provided in Steps~$2$ and $3$ to
calculate the parameters of the controller to be synthesised (Step~C). 
Finally, DSSynth builds an intermediate ANSI-C code for the digital system
implementation, which is used as input for the CEGIS engine (Step~D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
property of interst (i.e., robust stability) and is passed to the
Counterexample-Guided Inductive Synthesis (CEGIS) module of
CBMC~\cite{ClarkeKL04}, where the controller is marked as the input variable
to synthesise.  The properties specified in the ANSI-C code model can only
be satisfied if CEGIS synthesises controller coefficients that
satisfy~$\phi$.  CEGIS employs an iterative, counterexample-guided
refinement process which is explained in detail in
section~\ref{synthesiser-general}.  A~successful synthesis result is
reported if CEGIS generates a controllerthat is safe with respect to~$\phi$. 
In particular, the ANSI-C code model guarantees that a synthesised solution
is complete and sound with respect to stability property~$\phi$, since it
does not depend on system inputs and outputs.  In the case of stability, the
specification~$\phi$ consists in a number of assumptions on the polynomial
coefficients, following Jury's Criteria, as well as the restrictions set in
the representation of these coefficients.
